---
title: "Analytical Plan for Association between leadership commitment and professional development at NASA (2020): unweighted sex-adjusted stratified analysis"
subtitle: 'DOCUMENT: SAP-2022-011-GJ-v01'
author: '**From:** Felipe Figueiredo **To:** techsavvy32 (fiverr.com)'
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    reference_docx: misc/style_SAP_en.docx
    toc: yes
# toc-title: "Sumário"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
options(scipen = 999)
library(pander)
library(knitr)
panderOptions('table.style', 'rmarkdown')
panderOptions('table.split.table', 160)
```

---

\newpage

**Analytical Plan for Association between leadership commitment and professional development at NASA (2020): unweighted sex-adjusted stratified analysis**

**Document version**

```{r history}
Version <- c("01")
Changes <- c("Initial version")
history <- cbind(Version, Changes)
colnames(history) <- c("Version", "Alterations")
# pander(history, split.cells = 70)
kable(history)
```

---

# Abbreviations

- BMI: body mass index
- CI: confidence interval
- CV: coefficient of variation
- d: Cohen's D effect size
- HR: hazards ratio
- IQR: interquartile range
- IRR: incidence rate ratio
- OR: odds ratio
- RR: risks ratio
- SD: standard deviation

# Context

## Objectives

Quantify the association between leadership commitment and
employee professional development
at NASA from the 2020 Federal Employee Viewpoint Survey, disregarding the FEVS survey weights.

## Hypotheses

## Study design

# Data

```{r cleaning, include=FALSE}
source("scripts/input.R", encoding = 'UTF-8')
```

## Raw data

## Analytical dataset

All variables in the analytical set were labeled according to the raw data provided and values were labeled according to the data dictionary for the preparation of production-quality results tables and figures.

After the cleaning process `r ncol(analytical)` variables were included in the analysis with `r nrow(analytical)` observations.
Table 1 shows the structure of the analytical dataset.

```{r analytical data}
analytical_mockup %>%
  pander(caption = "**Table 1** Analytical dataset structure after variable selection and cleaning.")
```

The analytical dataset will be included in the private version of the report, and will be omitted from the public version of the report.

# Study variables

## Primary and secondary outcomes

**Specification of outcome measures** (Zarin, 2011):

1. (Domain)
2. (Specific measurement)
3. (Specific metric)
4. (Method of aggregation)

**Primary outcome**

## Covariates

# Statistical methods

## Statistical analyses

### Descriptive analyses

The epidemiological profile of the study participants will be described.
Demographic
(sex, age and BMI)
and clinical variables
<!-- ( [vars] ) -->
will be described as
mean (SD)
<!-- median (IQR) -->
or as counts and proportions (%), as appropriate.
The distributions of participants' characteristics will be summarized in tables and visualized in exploratory plots.

### Inferential analyses

All comparisons between groups will be performed as univariate analyses.
Continuous variables will be compared between groups with the
independent t test with Welch correction.
<!-- paired t test. -->
<!-- Wilcoxon test. -->
Differences in distribution of categorical variables will be assessed with the
Fisher exact test.
<!-- chi-square test. -->
<!-- McNemar test. -->

<!-- All inferential analyses will be performed in the statistical models (described in the next section). -->

### Statistical modeling

### Missing data

No missing data imputation will be performed.
All evaluations will be performed as complete case analyses.

## Significance and Confidence Intervals

All analyses will be performed using the significance level of 5%.
All significance hypothesis tests and confidence intervals computed will be
two-tailed.
<!-- left-tailed. -->
<!-- right-tailed. -->

## Study size and Power

N/A

## Statistical packages

This analysis will be performed using statistical software `R` version `r getRversion()`.

# Observations and limitations

# References

- **SAR-2022-011-GJ-v01** -- Association between leadership commitment and professional development at NASA (2020): unweighted sex-adjusted stratified analysis
<!-- - Cohen, J. (1988). Statistical power analysis for the behavioral sciences (2nd Ed.). New York: Routledge. -->
- Zarin DA, et al. The ClinicalTrials.gov results database -- update and key issues. N Engl J Med 2011;364:852-60 (<https://doi.org/10.1056/NEJMsa1012065>).
- Gamble C, et al. Guidelines for the Content of Statistical Analysis Plans in Clinical Trials. JAMA. 2017;318(23):2337–2343 (<https://doi.org/10.1001/jama.2017.18556>).

# Appendix

This document was elaborated following recommendations on the structure for Statistical Analysis Plans (Gamble, 2017) for better transparency and clarity.

## Availability

Both this analytical plan and the corresponding analysis report (**SAR-2022-011-GJ-v01**) can be downloaded in the following address:

<https://philsf-biostat.github.io/SAR-2022-011-GJ/>

<!-- The client has requested that this analysis be kept confidential. -->
<!-- Both this analytical plan and the corresponding analysis report (**SAR-2022-011-GJ-v01**) are therefore not published online and only the title and year of the analysis will be included in the consultant's Portfolio. -->
<!-- The portfolio is available at: -->

<!-- <https://philsf-biostat.github.io/> -->
